FLM for growth as function of SPEI

### 2021-01-08 analysis/paper/vital rate models.Rmd
change axes on plots

```{r}
g_post_cf <-
  gam(shts_next ~ 
        s(log_shts) + #does this *need* to be log # shoots?
        # s(year, bs = "re") + #random effect of year
        s(plot, bs = "re") + #random effect of plot
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal-ish response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_cf,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
plot(g_post_cf, pages=1)
```

@@

```{r}
g_post_1ha <-
  gam(shts_next ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_1ha,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

@@

```{r}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_shts = log(mean(shts, na.rm = TRUE)),  #log of mean shoots, not mean of log_shts
                   plot = "newlevel")
# exp(1.032814) # 2.8 shoots
```

@@

Lag labels

```{r}
# first column is February, the month of the census
labs <- c("Feb", "Jan", paste0(month(12:1, label = TRUE), " (y-1)"), paste0(month(12:2, label = TRUE), " (y-2)"))
```

@@

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_growth_cf
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_growth_1ha
```

@@

```{r}
p_growth_cf_slice <-
  pred_g_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "Continuous Forest", y = "shoots (t+1)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_growth_cf_slice
```

```{r}
p_growth_1ha_slice <-
  pred_g_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "1-ha Fragments", y = "shoots (t+1)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_growth_1ha_slice
```

@@

foo <- function(x) {
  d <- 1:25
  names(d)<-labs
  x <- as.numeric(x)
  # s <- glue("lag {x} ({names(d[x])})")
  s <- names(d[x])
  return(s)
}

p_growth_cf_months <-
  plotdf %>% 
  ggplot(aes(x = x, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("SPEI3") +
  scale_y_continuous("shoots (t+1)") +
  facet_wrap(~lag, labeller = as_labeller(foo)) +
  theme_bw()
```

@@

```{r}
s_post_cf <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
anova(s_post_cf)
```

```{r}
s_post_1ha <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
anova(s_post_1ha)
```

@@

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_surv_cf
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_surv_1ha
```

@@

```{r}
p_surv_cf_slice <-
  pred_s_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "Continuous Forest", y = "P(survival)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_surv_cf_slice
```

```{r}
p_surv_1ha_slice <-
  pred_s_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "1-ha Fragments", y = "P(survival)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_surv_1ha_slice
```

@@

### Fit GAMs
```{r}
x <- demog_post_cf$flowered
sum(x, na.rm = TRUE) / length(x)
```

```{r}
f_post_cf <-
  gam(flowered ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
f_post_1ha <-
  gam(flowered ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
```
Something is wrong.  Flowering probability should not be 1.

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous("lag (months)", breaks = 0:24, labels = labs, expand = c(0,0)) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
```

@@

```{r}
p_flowered_cf_slice <-
  pred_f_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "Continuous Forest", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# p_surv_cf_slice
```

```{r}
p_flowered_1ha_slice <-
  pred_f_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "1-ha Fragments", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# p_surv_1ha_slice
```

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth of average sized plant (~2.8 shoots)") +
  plot_layout(guides = "collect") & theme_talk
p_growth_spei
ggsave(here("growth_spei_xa.png"), p_growth_spei, height = 7, width = 14)
```

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk
p_surv_spei
ggsave(here("surv_spei_xa.png"), p_surv_spei, width = 14, height = 7)
```

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk
p_flowered_spei
ggsave(here("flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```

>>>>

```{r}
g_post_cf <-
  gam(shts_next ~ 
        s(log_shts) + 
        s(plot, bs = "re") + #random effect of plot
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal-ish response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_cf,
      # gamma = 1.2, #I maybe need to optimize this with cross-validation?
      method = "REML")
```

@@

```{r}
plot(g_post_cf, select = 1, main = "select = FALSE")
```

@@

```{r}
g_post_1ha <-
  gam(shts_next ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
plot(g_post_1ha, select = 1)
```

@@

```{r}
# use mean size plant across both habitats so plots are comparable
ref_data <-
  demog_post %>%
  dplyr::summarize(log_shts = log(mean(shts, na.rm = TRUE)),  #log of mean shoots, not mean of log_shts
                   plot = "newlevel")
# exp(1.032814) # 2.8 shoots
mean_size <- round(exp(ref_data$log_shts), 1)
```

@@

@@

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_cf
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_1ha
```

@@

```{r}
p_growth_cf_slice <-
  pred_g_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "Continuous Forest", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_cf_slice
```

```{r}
p_growth_1ha_slice <-
  pred_g_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "1-ha Fragments", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_1ha_slice
```

@@

foo <- function(x) {
  x <- as.numeric(x)
  mon <- month(ymd("2020-2-01") - months(x), label = TRUE)
  l <- glue("lag={x} ({mon})")
  return(l)
}

p_growth_cf_months <-
  plotdf %>% 
  ggplot(aes(x = x, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("SPEI3") +
  scale_y_continuous("shoots (t+1)") +
  facet_wrap(~lag, labeller = as_labeller(foo)) +
  theme_bw()
p_growth_cf_months
```

@@

```{r}
s_post_cf <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
# gam.check(s_post_cf) #not sure what to expect from any of these plots
```
```{r}
summary(s_post_cf)
```

```{r}
s_post_1ha <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
summary(s_post_1ha)
```

@@

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_cf
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_1ha
```

@@

```{r}
p_surv_cf_slice <-
  pred_s_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "Continuous Forest", y = "P(survival)") +
  theme_linedraw()
p_surv_cf_slice
```

```{r}
p_surv_1ha_slice <-
  pred_s_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "1-ha Fragments", y = "P(survival)") +
  theme_linedraw()
p_surv_1ha_slice
```

@@

```{r}
x <- demog_post_cf$flowered
sum(x, na.rm = TRUE) / length(x)
```

Around 0.05 percent of plants flowered.

```{r}
f_post_cf <-
  gam(flowered ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
plot(f_post_cf, select = 1, trans = plogis)
```

Plants with exp(3) = 20 shoots have close to a 100% chance of flowering.

```{r}
f_post_1ha <-
  gam(flowered ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
plot(f_post_1ha, select = 1, trans = plogis)
```

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
```

Something is wrong.  Flowering probability should not be 1 for an average-sized plant.

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
```

@@

```{r}
p_flowered_cf_slice <-
  pred_f_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "Continuous Forest", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_flowered_cf_slice
```

```{r}
p_flowered_1ha_slice <-
  pred_f_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("", breaks = 0:24, labels = labs) +
  labs(title = "1-ha Fragments", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_flowered_1ha_slice
```

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth of average sized plant (~2.8 shoots)") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
ggsave(here("growth_spei_xa.png"), p_growth_spei, height = 7, width = 14)
```

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
ggsave(here("surv_spei_xa.png"), p_surv_spei, width = 14, height = 7)
```

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
ggsave(here("flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```
